resistanceModelNotesAndy

### 2015-07-08 resistanceModelNotesAndy.Rmd
notes

@@

1. should I create a little shiny app allowing the mixture & sequential scenarios to be compared ?

>>>>

** 7/7/15 **
new version of UI comparing scenarios with greater differences in dominance.
Still doesn't produce something similar to curtis fig2 where mixture does much better.

@@

1. should I create a little shiny app mimicing curtis fig2, & allowing usr to modify params, to see how to keep the mixtures doing better ?
